---
title: "Quiz 3 Start"
author: "Anthony Landas"
date: "February 26, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(devtools)
library(roxygen2)
library(readr)
```

## Intro

I'm building an R package using devtools `create` function

Name the package: `r pname<-"LATools"`

Now let's run the script

```{r}
devtools::create(pname)
```


## Defaults

First we want fill out the `DESCRIPTION` file.

```{r}
pname<-"LATools"
devtools::create(pname)
dir(pname)

loc<-paste(getwd(),pname,sep="/")
loc_pack <-paste(loc,"DESCRIPTION",sep="/")
readLines(loc_pack)
#loc<-getwd()
#loc_pack<-paste(loc, pname, sep="/")
#readLines(loc_pack)

desc<-readLines(paste(loc_pack))

desc[grep("Title",desc)]<-"Title: Landas Anthony Tools"
desc[grep("Author",desc)]<-"Authors@R: person(\"Tony\", \"Landas\", email = \"landa057@umn.edu\", role = c(\"aut\", \"cre\"))"
desc[grep("Description",desc)]<-"Description: This is a set of functions, etc for Quiz and HW."
desc[grep("License",desc)]<-"License: MIT + file LICENSE"
writeLines(desc, con=loc_pack, sep ="/")

```

'LICENSE' file
```{r}
write_file(x="
YEAR: 2018
COPYRIGHT HOLDER: Tony Landas
", path=paste(loc,"LICENSE",sep="/"))
```

## Functions

Let's just creat an R file to edit.

```{r}
filename<-"Funcs.R"

write_file(" 
#' TITLE
#'
#' @par x is data
#'
#' Desc
#' @export
#' @example logL(x, binomial, c(-100, 100))
logL <-function(x, fun, int)
{
  LL <- function(theta)#Theta Est
  {
   sum(fun(theta, x))
  }

  MLE <- optimize(LL, maximum = TRUE, int)#Likelihood Est
  return(MLE$maximum)
}
 

ggplotW <- function(d, xcol, ycol, colorVar)
{
  plot <- ggplot(data=d, aes(x = xcol, y = ycol, color = colorVar)) + geom_point()
  print(plot)
  return(plot)
} 

spread <- function(d)
{
  moo = sum(d$x* d$p)
  
  sig2 = (sum(d$x - moo)^2) * d$p
  
  sD = sqrt(sig2)
}

spreadCheck <- function(d)
{
  stopifnot(length(d$x) != 0)#Value Checks for x
  stopifnot(is.finite(d$x))
  stopifnot(is.numeric(d$x))
  stopifnot(length(d$p) != 0)#p
  stopifnot(is.finite(d$p))
  stopifnot(is.numeric(d$p))
  stopifnot(all.equal(1, sum(d$p)))
  
  moo = sum(d$x * d$p)
  
  sig2 = sum(((d$x - moo)^2) * d$p)
  
  sD = (sqrt(sig2))
  
  list(mu = moo, variance = sig2, StandarDev = sD)
}

myapply <- function(X, MARGIN, FUN, ...)
{
  R = dim(X)[1]
  C = dim(X)[2]
  f = match.fun(FUN)
  
  if (MARGIN == 1)
  {
    result = list()
    for (i in 1:R)
    {
      result[[i]] = f(X[i,], ...)
    }
  }
  else if(MARGIN == 2)
  {
    result = list()
    for (j in 1:C)
    {
      result [[j]] = f(X[, j], ...)
    }
  }
  return(simplify2array(result))
}
",path=paste(loc,"R",filename,sep="/"))

```

## Mannuals

Here we will use the `document` function in devtools to build Help  files using `roxygen2` syntax. 

```{r}
devtools::document(loc)
```

## Vignette

```{r}
devtools::use_vignette("Explanation", loc)
```

## Data
```{r}
flights <-read.csv("http://users.stat.umn.edu/~almquist/3811_examples/all_alaska_flights.csv")
d <- read.table(url("http://www.stat.umn.edu/geyer/3701/data/q1p4.txt"), header = TRUE)
setwd("LATools")
gap <-read.csv("http://users.stat.umn.edu/~almquist/3811_examples/gapminder2007ex.csv", header = TRUE)

devtools::use_data(gap, d, flights, pkg = loc, overwrite = TRUE)

write_file(x=
             "
           #' Example data from class
           #' 
           #' @author Charlie Geyer \\email{geyer@umn.edu}
           #' @references\\url{http://users.stat.umn.edu/~almquist/3811_examples/gapminder2007ex.csv}  
           \"gap\" 
           
           #' @author Charlie Geyer \\email{geyer@umn.edu}
           #' @references\\url{http://www.stat.umn.edu/geyer/3701/data/q1p4.txt}  
           \"d\" 
           
           #' @author Charlie Geyer \\email{geyer@umn.edu}
           #' @references\\url{http://users.stat.umn.edu/~almquist/3811_examples/all_alaska_flights.csv}
           \"flights\" ",path=paste(loc,"R","data.R",sep="/"))


devtools::document(loc)
```

## Testing
```{r}
#setwd("LATools")
#use_testthat(loc_pack)

write_file(x="
context(\"Log Likelihood Estimater\")
test_that(\"x is data, fun is a distribution, int is an interval\", {
  binomial <- function(theta, x) {dbinom(x, 20, prob = 1 / (1 + exp(- theta)), log = TRUE)}
  logL(flights, binomial, c(-100,100))
})
",path="tests/testthat/test_LogL.R")

write_file(x="
context(\"Plot Creator\")
test_that(\"x is data\", {
  
})
",path="tests/testthat/test_GGPW.R")

write_file(x="
context(\"spread calaculates mu, variance and standard deviation\")
test_that(\"The 3 functions calculate correctly\", {
  spreadL <- list(moo=mean(d), var=var(d), sd=sqrt(var(d)))
  expect_identical(spread(d), spreadL)
})
",path="tests/testthat/test_spread.R")

write_file(x="
context(\"spreadCheck calaculates mu, variance and standard deviation, with GIEMO\")
test_that(\"The 3 functions calculate correctly and GIEMO catches errors\", {
  spreadL <- list(moo=mean(d), var=var(d), sd=sqrt(var(d)))
  expect_identical(spread(d), spreadL)

  Nope <- try(func2(NA),silent=TRUE)
})
",path="tests/testthat/test_spreadCheck.R")
```

## Dependencies
```{r}
use_package("ggplot2",pkg=loc)
use_package("dplyr", pkg=loc)

```

##Builds

```{r}
devtools::check(loc)
devtools::build(loc)
devtools::install(loc)
```
